---
title: "Downloading Stock Prices in R"
output: html_notebook
---

### Install and load [dplyr](https://dplyr.tidyverse.org/), [tidyquant](%22https://cran.r-project.org/web/packages/tidyquant/index.html%22), and [ggplot2](%22https://ggplot2.tidyverse.org/%22)

```{r}
if (!require("dplyr", quietly = TRUE)) {
  install.packages("dplyr")
  library(dplyr)
}
if (!require("tidyquant", quietly = TRUE)) {
  install.packages("tidyquant")
  library(tidyquant)
}
if (!require("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
  library(ggplot2)
}
```

### 1. Download the stock prices for a single stock using tidyquant

```{r}
AAPL <- tq_get('AAPL',
               from = "2020-01-01",
               to = Sys.Date(),
               get = "stock.prices")
```

#### 1.1 Print the head and tail to review the downloaded data

```{r}
print(rbind(head(AAPL), tail(AAPL)))
```

### 1.2a Chart the historical stock price using quaintmod

```{r}
chart_Series(AAPL['2020-01/2024-08'])
```

### 1.3b Chart the historical stock price using ggplot

```{r}
aapl %>%
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  theme_classic() +
  labs(x = 'Date',
       y = "Adjusted Price",
       title = "Apple price chart") +
  scale_y_continuous(breaks = seq(0,300,10))
```

### 1.4 Save the plot as a png

```{r}
pdf(file = 'aapl.pdf')
aapl %>%
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  theme_classic() +
  labs(x = 'Date',
       y = "Adjusted Price",
       title = "Apple price chart") +
  scale_y_continuous(breaks = seq(0,300,10))
dev.off()
```

### 1.5 Write the data to a text file

```{r}
write.table(AAPL, "AAPL.txt", row.names = FALSE)
```

### 2. Download the stock prices for multiple stocks

```{r}
tickers = c("AAPL", "QQQ", "SPY", "VOO", "VTI", "HIMS")

prices <- tq_get(tickers,
                 from = "2020-01-01",
                 to = Sys.Date(),
                 get = "stock.prices")
```

### 2.1 Review the downloaded data

```{r}
prices %>%
  group_by(symbol) %>%
  slice(1)
```

### 2.2 Chart the historical stock prices using ggplot

```{r}
prices %>%
  ggplot(aes(x = date, y = adjusted, color = symbol)) +
  geom_line() +
  facet_wrap(~symbol,scales = 'free_y') +
  theme_classic() +
  labs(x = 'Date',
       y = "Adjusted Price",
       title = "Price Chart") +
  scale_x_date(date_breaks = "month",
               date_labels = "%b\n%y")
```

### 2.3 Save the plot as a pdf

```{r}
pdf(file = 'prices.pdf')
prices %>%
  ggplot(aes(x = date, y = adjusted, color = symbol)) +
  geom_line() +
  facet_wrap(~symbol,scales = 'free_y') +
  theme_classic() +
  labs(x = 'Date',
       y = "Adjusted Price",
       title = "Price Chart") +
  scale_x_date(date_breaks = "month",
               date_labels = "%b\n%y")
dev.off()
```

### 2.4 Write the data to a text file

```{r}
write.table(prices, "prices.txt", row.names = FALSE)
```
